\bf Focusing on Fast Neural Network Inference

### 2018-05-16 wnmt.2018/wnmt.tex
small numerical differences

We experimented with varying the vocabulary size and the RNN state size before settling for a vocabulary size of 30,000 (for both source and target language) and 256 for the state size, Figure~\ref{tab:BLEU for newstest2014}.

\begin{table}
\begin{center}
\small
\begin{tabular}{|l|r|r|r|} \hline
		& \multicolumn{3}{|c|}{\emph{State dim}}	\\ \hline	
Vocab size	& 256	& 512	& 1024 \\ \hline
1000 		& 10.9 	& 	& 11.8 \\ 
5000		& 15.9	&  	& 16.4 \\ 
10000		& 17.2	& 	& 17.9 \\
20000		& -	&	& 18.4 \\ 
30000		& 17.8	& 18.5	& 18.7 \\ \hline
\end{tabular}
\end{center}
\caption{Test set BLEU (newstest2014) for hyper-parameters}
\label{tab:BLEU for newstest2014}
\end{table}

@@

Our second system uses multiplicative-LSTM in the encoder and the first layer of a decder, and a GRU in the second layer. We trained 2 systems with differing vocabulary sizes using an extension of the Nematus toolkit which supports such model.

>>>>

We experimented with varying the vocabulary size and the RNN state size before settling for a vocabulary size of 30,000 (for both source and target language) and 256 for the state size, Table~\ref{tab:BLEU for newstest2014}.

\begin{table}
\begin{center}
\begin{tabular}{|l|r|r|r|} \hline
		& \multicolumn{3}{|c|}{\emph{State dim}}	\\ \hline	
Vocab size	& 256	& 512	& 1024 \\ \hline
1000 		& 12.23 &	& 12.77 \\ 
5000		& 16.79	&  	& 17.16 \\ 
10,000		& 18.00	& 	& 18.19 \\
20,000		& -	&	& 19.52 \\ 
30,000		& 18.51	& 19.17	& 19.64 \\ \hline
\end{tabular}
\end{center}
\caption{Validation set BLEU (newstest2014) for GRU-based model}
\label{tab:BLEU for newstest2014}
\end{table}

@@

Our second system uses multiplicative-LSTM in the encoder and the first layer of a decder, and a GRU in the second layer, using an extension of the Nematus toolkit which supports such model. We trained 2 systems with differing vocabulary sizes and varied the beam sizes before chose the the settings that produces good translation quality on the validation set, Table~\ref{tab:mLSTM BLEU - vocab sizes}.

\begin{table}
\small
\begin{center}
\begin{tabular}{|l|r|r|r|r|r|} \hline
		& \multicolumn{5}{|l|}{\emph{Beam size}}	\\ \hline	
Vocab size	& 1	& 2	& 2	& 4	& 5 \\ \hline
40,000 		& 23.45	& 24.15	& 24.48	& 24.42	& 24.48 \\ 
50,000		& 23.32	& 24.04	& 	&	& \\ \hline
\end{tabular}
\end{center}
\caption{Validation set BLEU for mLSTM-based model}
\label{tab:mLSTM BLEU - vocab sizes}
\end{table}

\section{Result}
\label{sec:Result}
